The Exoplanet Orbit Database 2, 2014 updates

### 2014-03-10 draft/ms.tex
Done with section 2

{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
the unit of degree. We report the projected spin-orbit misalignment of
transiting systems, which is measured by, e.g., the Rossiter-McLaughlin
effect or planet transiting star spots ZZZ add references for RM effect and the star spot method. $\lambda$ is introduced because the true spin-orbit angle
($\phi$), defined as the angle between the stellar spin axis and the
orbital axis, is normally not directly measurable. We follow the
definition of $\lambda$ in \cite{Fabrycky2009} where the
coordinates are defined as follows; the $z$-axis points toward the
observer, the $x$-axis points along the intersection of the sky plane
and the planet's orbital plane with the ascending node of the planet
having $x<0$, and the $y$-axis completes a right
handed-triad. $\lambda$ is measured clockwise on the sky from the
$y$-axis to the projected stellar rotational axis. $\lambda$ is not a newly added field but we describe it here because $\lambda$'s were not reported consistently since some literatures
report $\beta = -\lambda$ instead. We sorted these cases out and made
sure that our $\lambda$'s are following the definition of \cite{Fabrycky2009}.
%------------------------------------------------------------------------------
\subsection{Transit Parameters}\label{sec:transit}

@@

{\bf SHK} is the Mount Wilson Ca II S-value and {\bf RHK} is the Chromospheric activity of star as $\log{R'_{HK}}$
: field previously reported the  and
now it is changed to SHK.  ; ZZZ What's the source for SHK and RHK?
Still discovery paper and Butler 2006? ZZZ SHK is a poorly maintained
field, and it is unreferenced at the moment though we plan to include
proper reference in the future.

@@

%------------------------------------------------------------------------------
\subsection{Revised and Removed Fields}

We have major updates by taking out some of the fields and by revising the existing fields. Here, we explain why we removed or revised such fields.

{\bf SPSTAR} field previously reported the stellar type of the host
star. We choose to remove this field because....? - stellar type of
star (unvetted), gone;

{\bf NSTEDID} field reported ID of host star in NStED and now it is
replaced by EANAME, which is the name of the star as appears on the
Exoplanet Archive.

{\bf MASSREF} and {\bf MASSURL} fields were used to report the
reference and the url of stellar mass but now they are used for planet
mass.

%------------------------------------------------------------------------------
Figure: Figure of single planet page, to show updated transit
parameters and RV curves etc.?

@@

>>>>

{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
the unit of degree. We report the projected spin-orbit misalignment of
transiting systems, which is measured by, e.g., the Rossiter-McLaughlin
effect or planet transiting star spots ZZZ add references for RM effect and the star spot method. $\lambda$ is introduced because the true spin-orbit angle
($\phi$), defined as the angle between the stellar spin axis and the
orbital axis, is normally not directly measurable. We follow the
definition of $\lambda$ in \cite{Fabrycky2009} where the
coordinates are defined as follows; the $z$-axis points toward the
observer, the $x$-axis points along the intersection of the sky plane
and the planet's orbital plane with the ascending node of the planet
having $x<0$, and the $y$-axis completes a right
handed-triad. $\lambda$ is measured clockwise on the sky from the
$y$-axis to the projected stellar rotational axis. $\lambda$ is not a newly added field but we describe it here because $\lambda$'s were not reported consistently since some literatures
report $\beta = -\lambda$ instead. We sorted these cases out and made
sure that our $\lambda$'s are following the definition of \cite{Fabrycky2009}.

{\bf MASSREF} and {\bf MASSURL} fields were used to report the
reference and the URL of stellar mass but now they are used for planet
mass.
%------------------------------------------------------------------------------
\subsection{Transit Parameters}\label{sec:transit}

@@

@@

SHK and RHK are poorly maintained fields and they unreferenced at the moment though we plan to include
proper reference in the future. Most of the values are from \cite{Butler2006}.

%------------------------------------------------------------------------------
\subsection{Removed Fields}

We removed 2 fields.

{\bf SPSTAR} field previously reported the stellar type of the host
star but it is removed since it is not reliable.

{\bf NSTEDID} field reported ID of host star in NStED and now it is
replaced by EANAME, which is the name of the star as appears on the
NASA's Exoplanet Archive \citep{Akeson2013}.

%------------------------------------------------------------------------------
ZZZ Figure: Figure of single planet page, to show updated transit
parameters and RV curves etc.?

@@

We included KOIs and other planets and describe the criteria for other planets.

KOI's are not counted as part of the EOD due to their status of being 'candidates', we include them in our website so that these KOIs are put into the context of all confirmed exoplanets. To display the KOIs in the EDE table, check the 'Kepler' option on the upper left of the table (default selection only includes 'Orbit Database' and 'Other'). The KOIs listed in our table include two past Kepler data releases and the most up-to-date release from January 2013. The original data are from the NASA Exoplanet Archive.
